COG-ED Manuscript

### 2022-02-17 06_Paper/COG-ED/Manuscript.Rmd
moved all analyses to other script

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

@@

  # load here-library for path-independent project structure (install here by calling install.packages("here") if necessary)
  # set top level directory to source file

  library(here)

  # load reproducible environment library to get all packages with correct versions form the renv.lock file
  # install renv by calling install.packages("renv") if necessary

  library(renv)

  renv::init(here("06_Paper","COG-ED"))

  # the required packages are:
  # "bibtex", "here", "tidyverse", "bayestestR", "papaja", "lmerTest", "afex", "emmeans", "sjPlot",
  # "kableExtra", "interactions", "glmmTMB", "BayesFactor", "ggplot2", "egg", "knitr", "effectsize", and "MuMIn"

  # sets orthogonal contrasts for mixed-effects model and rmANOVA globally in order to get meaningful Type-III tests

  set_sum_contrasts()

```{r import, echo=FALSE, message=FALSE, warning=FALSE}

@@

  # import n-back and effort discounting data into a list each

  datalist_nback = lapply(list.files(here("04_RawData", "pilot", "COG-ED"), pattern = '.*nback.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
  datalist_ED = lapply(list.files(here("04_RawData", "pilot", "COG-ED"), pattern = '.*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

  # create empty data frames for loops to feed into

  data_nback <- data.frame(subject = character(), level = double(), target = character(),
                           response = character(), correct = double(), rt = double())
  data_ED <- data.frame(subject = character(), step = double(), choice = character(),
                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())

  # put relevant data into data frames

  for (i in 1:length(datalist_nback)) {

    newdata <- data.frame(datalist_nback[[i]][["Participant"]], datalist_nback[[i]][["currentlevel"]],
                          datalist_nback[[i]][["Stimulus"]], datalist_nback[[i]][["trial_resp.keys"]],
                          datalist_nback[[i]][["trial_resp.corr"]], datalist_nback[[i]][["trial_resp.rt"]])
    colnames(newdata) <- names(data_nback)
    data_nback <- rbind(data_nback, newdata)
  }

  for (i in 1:length(datalist_ED)) {

    newdata <- data.frame(datalist_ED[[i]][["Participant"]][2:length(datalist_ED[[i]][["Participant"]])],
                          datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
                          datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
                          datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
                          datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
                          datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
                          datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])
    colnames(newdata) <- names(data_ED)
    data_ED <- rbind(data_ED, newdata)
  }

  # change the name of a subject (it has the suffix "_neu" because the paradigm didn't start properly the first time)

  data_nback$subject[data_nback$subject == "E12K08_neu"] <- "E12K08"
  data_ED$subject[data_ED$subject == "E12K08_neu"] <- "E12K08"

  # remove one subject who did not understand the instructions of the n-back task and reacted only to every n-th stimulus

  data_nback <- data_nback[data_nback$subject != "M28B11", ]
  data_ED <- data_ED[data_ED$subject != "M28B11", ]

  # replace some columns with 'easy to work with' values

  # the target column will contain 1 for targets and 0 for all non-targets

  data_nback[data_nback == "Target"] <- 1
  data_nback[data_nback == "Pretarget"|data_nback == "Lure"|data_nback == "Distractor"] <- 0
  data_nback$target <- as.numeric(data_nback$target)

  # the response column will contain 1 for responses and 0 for all non-responses

  data_nback[data_nback == "left"|data_nback == "right"] <- 1
  data_nback[data_nback == "None"] <- 0
  data_nback$response <- as.numeric(data_nback$response)

  # for the multi level model to be able to assess the influence of post-error trials, we will include that as a regressor
  # so the nback data frame will contain a column of ones and zeros

  # add the "correct" column, but shifted down by one row

  data_nback$postcorrect = c(1,data_nback$correct[1:(length(data_nback$correct)-1)])

  # make sure to avoid transfer from the previous block by marking the first trial of each block as correct

  data_nback$postcorrect[c(1,seq(64,length(data_nback$postcorrect),64))] <- 1

  # correct subject code
  data_nback$subject[which(data_nback$subject == "E12K08_neu")] <- "E12K08"
  data_ED$subject[which(data_ED$subject == "E12K08_neu")] <- "E12K08"

  # the choice column will contain 1 for the left button and 2 for the right button

  data_ED[data_ED == "EDleftbutton"] <- 1
  data_ED[data_ED == "EDrightbutton"] <- 2
  data_ED$choice <- as.numeric(data_ED$choice)

  # since only the last choice of each comparison is relevant, we will keep only those rows

  data_ED <- data_ED[data_ED$step == 6,]
  data_ED <- subset(data_ED, select = -c(step))

  # import questionnaire data from RedCap

  data_quest <- read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
  colnames(data_quest)[1] <- "set" # rename the first column

  # remove the subject who misunderstood the instruction

  data_quest <- data_quest[data_quest$set != "M28B11", ]

  # remove unnecessary variables from questionnaire data frame

  data_quest <- subset(data_quest, select = -c(vl, date, preparatory_coged_complete, general_questions_timestamp, state,
                                               general_questions_complete, inclusion, inclusion_0___1, inclusion_0___2, inclusion_0_2,
                                               researcher_questions_complete, nasatlx_timestamp, nasatlx_complete, t1_psychopy_ed_csv,
                                               t1_psychopy_nback_csv, files_coged_complete, record_id_2, vl_er,
                                               date_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
                                               files_ered_complete, followup_ered_timestamp,
                                               nachb_01, nachb_01_inhalt, nachb_02, nachb_02_inhalt, nachb_03, nachb_07, nachb_07_inhalt,
                                               nachb_08, nachb_08_inhalt, nachb_08_haeufig, nachb_08_zurueck, followup_ered_complete,
                                               nfc_timestamp, nfc_complete, bis_11_timestamp, bis_11_complete, bscs_timestamp,
                                               bscs_complete, srs_timestamp, srs_complete, erq_erqse_timestamp, erq_erqse_complete,
                                               who5_timestamp, who5_complete, acs_timestamp, acs_complete, cdrisc_timestamp,
                                               cdrisc_complete, flexer_timestamp, flexer_complete))

  # compute index of rows in which the data sets change

  setindex <- c(1,which(data_quest$set != dplyr::lag(data_quest$set)),nrow(data_quest))

```{r SVcomputation, echo=FALSE, message=FALSE, warning=FALSE}

  # apply the addition or subtraction of 0.015625 to the last choices

  for (i in 1:nrow(data_ED)) {

    data_ED$fixedlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] == 2.00)] + 1]
    data_ED$flexlevel[i] <- data_ED[i,grep("Bvalue", colnames(data_ED))[which(data_ED[i,grep("Bvalue", colnames(data_ED))] != 2.00)] + 1]

    if (data_ED$choice[i] == 1) {
      if (data_ED$LBvalue[i] == 2.00) {
        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] + 0.015625, digits = 2)
      } else {
        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] - 0.015625, digits = 2)
      }
    } else {
      if (data_ED$RBvalue[i] == 2.00) {
        data_ED$flexvalue[i] <- round(data_ED$LBvalue[i] + 0.015625, digits = 2)
      } else {
        data_ED$flexvalue[i] <- round(data_ED$RBvalue[i] - 0.015625, digits = 2)
      }
    }

  }

  # create vector indicating in which rows the data of a new subject begins

  subjectindex <- c(1,which(data_ED$subject != dplyr::lag(data_ED$subject)),nrow(data_ED))

  # create empty data frame for the loop to feed into

  data_SV <- data.frame(subject = character(), level = double(), sv = double())

  # compute subjective values per n-back level and feed into data frame

  for (i in 1:(length(subjectindex)-1)) {

    # initialize empty vectors

    tempone <- double()
    temptwo <- double()
    tempthree <- double()
    tempfour <- double()

    # check for every number, whether it appears in the fixedlevel and flexlevel columns
    # divide flexvalue by 2 if it appears in the fixedlevel columns
    # append 1 if it appears in the flexlevel column

    # for 1-back

        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
          tempone <- append(tempone, data_ED$flexvalue[subjectindex[i]-1 +
                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)]/2)
        } else {
          # do nothing
        }

        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1)) == FALSE) {
          tempone <- append(tempone, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 1))))
        } else {
          # do nothing
        }

    # for 2-back

        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
          temptwo <- append(temptwo, data_ED$flexvalue[subjectindex[i]-1 +
                                                         which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)]/2)
        } else {
          # do nothing
        }

        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2)) == FALSE) {
          temptwo <- append(temptwo, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 2))))
        } else {
          # do nothing
        }

    # for 3-back

        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
          tempthree <- append(tempthree, data_ED$flexvalue[subjectindex[i]-1 +
                                                             which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)]/2)
        } else {
          # do nothing
        }

        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3)) == FALSE) {
          tempthree <- append(tempthree, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 3))))
        } else {
          # do nothing
        }

    # for 4-back

        if (is_empty(which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
          tempfour <- append(tempfour, data_ED$flexvalue[subjectindex[i]-1 +
                                                           which(data_ED$fixedlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)]/2)
        } else {
          # do nothing
        }

        if (is_empty(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4)) == FALSE) {
          tempfour <- append(tempfour, rep(1, length(which(data_ED$flexlevel[c(subjectindex[i]:(subjectindex[i+1]-1))] == 4))))
        } else {
          # do nothing
        }

    # put the mean subjective value of the three values per n-back level in the respective column and add to data frame

    newdata <- data.frame(subject = rep(data_ED$subject[subjectindex[i]],4),
                          level = c(1:4),
                          sv = c(mean(tempone), mean(temptwo), mean(tempthree), mean(tempfour)))
    data_SV <- rbind(data_SV, newdata)

  }

  # remove temporary variables

  remove(tempone, temptwo, tempthree, tempfour)

  # add the SVs trial-wise to the nback-data-frame for the multi-level-model

  for (i in 1:nrow(data_nback)) {

    data_nback$sv[i] <- data_SV$sv[data_SV$subject == data_nback$subject[i] & data_SV$level == data_nback$level[i]]

  }

```{r NFCcomputation, echo=FALSE, message=FALSE, warning=FALSE}

  # prepare temporary data frame for loop to feed into

  data_nfc <- data.frame(subject = character(), nfc = double())

  # compute index of rows in which the data sets change

  setindex <- c(1,which(data_quest$set != dplyr::lag(data_quest$set)),nrow(data_quest))

  # calculate NFC scores for every subject

  for (i in 1:(length(setindex)-1)) {

    nfc <- data_quest[setindex[i] + 2, grep("nfc", colnames(data_quest))]

    # define and invert items to be recoded

    nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] <-  nfc[ ,c(4,6,7,8,9,10,11,12,15,16)] * -1

    data_nfc <- rbind(data_nfc, data.frame(subject = data_quest$subject[setindex[i]],
                                           nfc = sum(nfc)))
  }

  # add the NFC scores trial-wise to the nback-data-frame for the multi-level-model

  for (i in 1:nrow(data_nback)) {

    data_nback$nfc[i] <- data_nfc$nfc[data_nfc$subject == data_nback$subject[i]]

  }

  # remove the temporary variables

  remove(nfc, data_nfc)

@@

```{r preprocessing, echo=FALSE, message=FALSE, warning=FALSE}

  # create new data frames for the specification curve analysis <!-- specification curve analysis has not been mentioned in the ms. so far -->
  # the data frame names are a combination of the letters from each of these categories, indicating how they will be preprocessed:
  #
  # across which dimensions the transformation and outlier exclusion will be done:
  #   (AA) across subjects, across n-back levels
  #   (AW) across subjects, within n-back levels
  #   (WW) within subjects, within n-back levels
  #   (WA) within subjects, across n-back levels
  # RT transformations:
  #   (R) raw/none
  #   (L) log
  #   (I) inverse
  #   (S) square-root
  # RT outlier exclusion:
  #   (N) none
  #   (2) 2 MADs from the median
  #   (5) 2.5 MADs from the median
  #   (3) 3 MADs from the median
  #   (O) 0-100 ms after stimulus onset
  #   (T) 0-200 ms after stimulus onset
  #
  # Example: the data frame "AWL3" has log-transformed RT data with no data points beyond 3 MADs
  # from the median
  #
  # Some combinations are nonsensical, so we will not include them: Raw data sets (__R__) with either no outlier
  # exclusion (___N_) or time-based outlier exclusion (___T_) do not need the different dimensions (A/W), and
  # time-based exclusion is nonsensical for transformed data sets.

  # create a list that contains the basic data frame of the n-back data for each of the pipelines

  pipelines_data <- replicate(63, data_nback, simplify = FALSE)
  pipelines_data <- setNames(pipelines_data, c("AARN","AAR2","AAR5","AAR3","AARO","AART",
                                               "AALN","AAL2","AAL5","AAL3",
                                               "AAIN","AAI2","AAI5","AAI3",
                                               "AASN","AAS2","AAS5","AAS3",
                                               "AWR2","AWR5","AWR3",
                                               "AWLN","AWL2","AWL5","AWL3",
                                               "AWIN","AWI2","AWI5","AWI3",
                                               "AWSN","AWS2","AWS5","AWS3",
                                               "WWR2","WWR5","WWR3",
                                               "WWLN","WWL2","WWL5","WWL3",
                                               "WWIN","WWI2","WWI5","WWI3",
                                               "WWSN","WWS2","WWS5","WWS3",
                                               "WAR2","WAR5","WAR3",
                                               "WALN","WAL2","WAL5","WAL3",
                                               "WAIN","WAI2","WAI5","WAI3",
                                               "WASN","WAS2","WAS5","WAS3"))

  for (i in 1:length(pipelines_data)) {

    # extract the name of the current data frame

    pipeline_name <- strsplit(names(pipelines_data)[i], "")

    # the first decision is whether transformations and exclusions will be applied across/within subjects/levels

    if (pipeline_name[[1]][1] == "A" & pipeline_name[[1]][2] == "A") {

          # the second decision is the type of transformation, depending on the third letter in the data frame name

          if (pipeline_name[[1]][3] == "L") {

            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
              log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
              log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

          } else if (pipeline_name[[1]][3] == "I") {

            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
              1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
              1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

          } else if (pipeline_name[[1]][3] == "S") {

            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
              sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
            pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
              sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])
          }

          # compute median and median absolute deviation

          pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
          pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)

          # the third decision is the outlier exclusion

          if (pipeline_name[[1]][4] == "2") {

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 2 * pipemad)
                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 2 * pipemad))), ]

          } else if (pipeline_name[[1]][4] == "5") {

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 2.5 * pipemad)
                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 2.5 * pipemad))), ]
          } else if (pipeline_name[[1]][4] == "3") {

            pipelines_data[[i]] <- pipelines_data[[i]][c(which(pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] < (pipemedian + 3 * pipemad)
                                                               & pipelines_data[[i]]$rt[pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] > (pipemedian - 3 * pipemad))), ]
          }

    } else if (pipeline_name[[1]][1] == "A" & pipeline_name[[1]][2] == "W") {

        # apply the transformations and exclusions across subjects but within levels

        for (x in 1:4) {

            # the second decision is the type of transformation, depending on the third letter in the data frame name

            if (pipeline_name[[1]][3] == "L") {

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

            } else if (pipeline_name[[1]][3] == "I") {

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

            } else if (pipeline_name[[1]][3] == "S") {

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0])

            }

            # compute median and median absolute deviation

            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)
            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1], na.rm = TRUE)

            # the third decision is the outlier exclusion

            if (pipeline_name[[1]][4] == "2") {

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

            } else if (pipeline_name[[1]][4] == "5") {

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

            } else if (pipeline_name[[1]][4] == "3") {

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
        }

    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "W") {

        # apply the transformations and exclusions within subjects and within levels

        for (x in 1:4) {

          for (y in 1:length(table(pipelines_data[[i]]$subject))) {

            # save the name of the subject as a temporary variable

            pipesubject <- names(table(pipelines_data[[i]]$subject))[y]

            # the second decision is the type of transformation, depending on the third letter in the data frame name

            if (pipeline_name[[1]][3] == "L") {

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                log10(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])

            } else if (pipeline_name[[1]][3] == "I") {

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                1/(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])

            } else if (pipeline_name[[1]][3] == "S") {

              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject])
              pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 &
                                       pipelines_data[[i]]$subject == pipesubject] <-
                sqrt(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 0 & pipelines_data[[i]]$subject == pipesubject])
            }

            # compute median and median absolute deviation

            pipemedian <- median(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)
            pipemad <- mad(pipelines_data[[i]]$rt[pipelines_data[[i]]$level == x & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 & pipelines_data[[i]]$subject == pipesubject], na.rm = TRUE)

            # the third decision is the outlier exclusion

            if (pipeline_name[[1]][4] == "2") {

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

            } else if (pipeline_name[[1]][4] == "5") {

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 2.5 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 2.5 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])

            } else if (pipeline_name[[1]][4] == "3") {

              ifelse(length(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                    (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))) > 0,
                     pipelines_data[[i]] <-
                       pipelines_data[[i]][-c(which(pipelines_data[[i]]$level == x & pipelines_data[[i]]$subject == pipesubject & pipelines_data[[i]]$response == 1 & pipelines_data[[i]]$correct == 1 &
                                                      (pipelines_data[[i]]$rt > (pipemedian + 3 * pipemad) | pipelines_data[[i]]$rt < (pipemedian - 3 * pipemad)))), ],
                     pipelines_data[[i]] <- pipelines_data[[i]])
            }
          }
        }

    } else if (pipeline_name[[1]][1] == "W" & pipeline_name[[1]][2] == "A") {

      # apply the transformations and exclusions within subjects but across levels

        for (y in 1:length(table(pipelines_data[[i]]$subject))) {

            # save the name of the subject as a temporary variable

            pipesubject <- names(table(pipelines_data[[i]]$subject))[y]

            # the second decision is the type of transformation, depending on the third letter in the data frame name

            if (pipeline_name[[1]][3] == "L") {

>>>>

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
always_allow_html : true
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}

@@

  # load libraries

  library(bibtex)       # for referencing, "bibtex" package
  library(here)         # for path independent file referencing, "here" package
  library(papaja)       # APA conform output, "papaja" package
  library(kableExtra)   # for great tables in R Markdown, "kableExtra" package
  library(interactions) # for simple slopes plots, "interactions" package
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package
  library(knitr)        # for including plots and such, "knitr" package
  library(effectsize)   # for effect sizes and CIs, "effectsize" package

@@

  # load the workspace variables that have been computed with the Analysis.R script

  load(here("06_Paper","COG-ED","Workspace.RData"))

@@
